Activity Monitoring Peer Assessment 1
========================================================

**Load Packages**
```{r, message=FALSE}
library(dplyr)
library(stringr)
library(reshape2)
library(mice)
library(lattice)
```
**Read Data**

```{r}
activity<-read.csv("activity.csv", header=T)
```

**Clean Data**
```{r, message=FALSE}
dly_steps<-select(activity, date, steps)
daily<-melt(dly_steps)
ds<-dcast(daily, date~., fun.aggregate=sum)
colnames(ds)[2]<-"steps"
```
**Mean Total Steps Taken Per Day?**
```{r fig.width=7, fig.height=6, message=FALSE}
library(dplyr)
library(stringr)
library(reshape2)
activity<-read.csv("activity.csv", header=T)
dly_steps<-select(activity, date, steps)
daily<-melt(dly_steps)
ds<-dcast(daily, date~., fun.aggregate=sum)
colnames(ds)[2]<-"steps"
hist(ds$steps)
```

The mean was 
`r as.integer(mean(ds$steps, na.rm=T))`

The median was
`r median(ds$steps, na.rm=T)`



**What is the average daily activity pattern?**

```{r fig.width=7, fig.height=6}
library(dplyr)
library(stringr)
library(reshape2)
activity<-read.csv("activity.csv", header=T)
adap<-select(activity, interval, steps)
adapmelt<-melt(adap, id.vars="interval")
adapcast<-dcast(adapmelt, interval~., fun.aggregate=mean, na.rm=T)
colnames(adapcast)[2]<-"steps"
adts<-as.ts(adapcast$steps, na.rm=T, frequency=1)
plot(adts)
```
Which time interval has the greatest average number of steps? The
`r adapcast$interval[which(adapcast$steps==max(adapcast$steps))]`th

**Imputing Missing Values**
What are the number of NAs?

Number of NAs can be found by 
```{r}
activity<-read.csv("activity.csv", header=T)
sum(is.na(activity))
```

A breakdown of course occurs in 
```{r}
summary(activity)
```
We will use the MICE package to impute

```{r, cache=TRUE, message=FALSE}
library(mice)
imp<-mice(activity)
impactivity<-complete(imp)

impdly_steps<-select(impactivity, date, steps)

impdaily<-melt(impdly_steps)
impds<-dcast(impdaily, date~., fun.aggregate=sum)
colnames(impds)[2]<-"steps"
```

Now we can graph the output and also look at the mean and median
```{r fig.width=7, fig.height=6}
hist(impds$steps)
```

The mean of the imputed steps is
`r as.integer(mean(impds$steps))`

The median of the imputed steps is
`r median(impds$steps)`

**Differences between Weekdays and Weekends?**
We will use the imputed dataset from now on.
```{r}
activity<-impactivity
activity$date<-as.Date(activity$date)
Weekends<-filter(activity, weekdays(activity$date)=="Saturday"|weekdays(activity$date)=="Sunday")
Weekdays<-filter(activity, weekdays(activity$date)!="Saturday"|weekdays(activity$date)!="Sunday")
Weekends<-select(Weekends, interval, steps)
wkd<-melt(Weekends, id.vars="interval")
wkends<-dcast(wkd, interval~., fun.aggregate=mean)
colnames(wkends)[2]<-"steps"
wkends<-as.ts(wkends$steps, frequency=1)

Weekdays<-select(Weekdays, interval, steps)
wky<-melt(Weekdays, id.vars="interval")
wkdys<-dcast(wky, interval~., fun.aggregate=mean)
colnames(wkdys)[2]<-"steps"
wkdys<-as.ts(wkdys$steps, frequency=1)


par(mfrow=c(2, 1))
plot(wkends)
plot(wkdys)
```